The effect of linking assumptions and number of response options on inferred scalar implicature rate

### 2018-04-30 writeup.Rmd
made visualization changes so axes are labeled and links are labeled like in paper

```{r load_packages, include = FALSE}
library(grid)
library(gtable)
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(jpeg)
library(lme4)
library(ggthemes)
library(forcats)
library(webppl)
# library(brms)
theme_set(theme_bw(18))
```

@@

# high definition only considers the highest point on the scale as "literal"
pragmatic_trials$high<-1
pragmatic_trials[pragmatic_trials$response=="Right",]$high <-0

# low definition only considers the lowers point on the scale as implicature 
pragmatic_trials$low<-0
pragmatic_trials[pragmatic_trials$response=="Wrong",]$low <-1

implicature_rate <- 
  pragmatic_trials %>% gather("definition","implicature", high:low)

@@

binary_plot<-
  binary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=15)) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

@@

ternary_plot<-
  ternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=15)) +
  scale_fill_manual(values = c("red4","grey", "springgreen3"), guide=FALSE)

@@

quaternary_plot<-
  quaternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE)

@@

quinary_plot<-
  quinary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE)

@@

```{r}
ggplot(results, aes(x=response,y=proportion)) +
  geom_bar(stat="identity") +
  facet_grid(response_type~trial_type, drop = TRUE) +
  theme_few()
```

@@

```{r implicatureResultss}
implicature_results<-
  implicature_rate %>%
  group_by(response_type, trial_type, implicature, definition) %>%
  summarize(counts = n()) %>%
  group_by(response_type, trial_type, definition) %>%
  mutate(total = sum(counts), proportion = counts/total)
```

```{r}
ggplot(implicature_results, aes(x=as.factor(implicature),y=proportion)) +
  geom_bar(stat="identity", position = "dodge") +
  facet_grid(response_type~definition + trial_type, drop = TRUE) +
  theme_few() + 
  labs(x="Implicature")
```

@@

implicature_analysis_a <- glmer(implicature ~ definition * response_type + trial_type + (1+response_type|card) + (1|participant), family="binomial", data=implicature_rate)

>>>>

```{r load_packages, include = FALSE}
library(grid)
library(gtable)
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(jpeg)
library(lme4)
library(ggthemes)
library(forcats)
library(webppl)
library(brms)
theme_set(theme_bw(18))
```

@@

# high definition only considers the highest point on the scale as "literal" (Weak link in paper)
pragmatic_trials$weak<-1
pragmatic_trials[pragmatic_trials$response=="Right",]$weak <-0

# low definition only considers the lowest point on the scale as implicature (Strong link in paper)
pragmatic_trials$strong<-0
pragmatic_trials[pragmatic_trials$response=="Wrong",]$strong <-1

implicature_rate <- 
  pragmatic_trials %>% gather("definition","implicature", weak:strong)

@@

binary_plot<-
  binary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="Response", y="Proportion of response")+
  theme_few() +
  theme(text = element_text(size=15)) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

@@

ternary_plot<-
  ternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="Response", y="Proportion of response")+
  theme_few() +
  theme(text = element_text(size=15)) +
  scale_fill_manual(values = c("red4","grey", "springgreen3"), guide=FALSE)

@@

quaternary_plot<-
  quaternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="Response", y="Proportion of response")+
  theme_few() +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 45, hjust = 1,vjust=1)) +
  scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE)

@@

quinary_plot<-
  quinary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="Response", y="Proportion of response")+
  theme_few() +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 45, hjust = 1, vjust=1)) +
  scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE)

@@

```{r}
ggplot(results, aes(x=response,y=proportion)) +
  geom_bar(stat="identity") +
  facet_grid(trial_type~response_type, drop = TRUE) +
  theme_few()
```

@@

```{r implicatureResultss}
implicature_results<-
  implicature_rate %>%
  group_by(response_type, trial_type, implicature, definition) %>%
  summarize(counts = n()) %>%
  group_by(response_type, trial_type, definition) %>%
  mutate(total = sum(counts), proportion = counts/total) %>%
  ungroup() %>%
  mutate(response_type=fct_relevel(response_type,"binary","ternary","quaternary","quinary"))

dodge = position_dodge(.9)
```

```{r}
ggplot(implicature_results[implicature_results$implicature == 1,], aes(x=definition,y=proportion,fill=definition)) +
  geom_bar(stat="identity") +
  facet_grid(trial_type~response_type, drop = TRUE) +
  theme_few() + 
  labs(x="Link",y="Inferred implicature rate")
```

@@

implicature_analysis_a <- glmer(implicature ~ definition * response_type * trial_type + (1|card) + (1|participant), family="binomial", data=implicature_rate)
